Handling String-Number Conversion in String Constraint Solving

### 2019-11-08 draft.tex
P(A) defined

\begin{lemma}\label{lemma:parikh}
For an PFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
\end{lemma}
%
Indeed, since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run. 
%
The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. \lh{say precisely how?}
%
For example, in the example of Figure~\ref{fig:sfa_def}, 
from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
\begin{lemma}\label{lemma:decx}
For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
\end{lemma}

Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$, 
we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encodes $w$. Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, 
hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them), we may say that 
%\begin{lemma}\ref{lemma:decw}
%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\parikhfof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
%\end{lemma}
 $$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$$
where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}.

\paragraph{Synchronisation of PFA}
The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$, 
namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.

>>>>

\begin{lemma}\label{lemma:parikh}
For an PFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
\end{lemma}
%
Indeed, since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run. 
%
The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. \lh{say precisely how?}
%
For example, in the automaton of Figure~\ref{fig:sfa_def}, 
from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
It is well known that the Parikh image of the language of $A$ can be efficiently computed in the form of linear arithmetic formula.
We will use $\parikhof{A}$ as a shorthand for $\parikhof{L(A)}$.

\begin{lemma}[\cite{PeterParikh}]
$\parikhof{A}$ of an FA $A$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$.
\end{lemma}

\begin{lemma}\label{lemma:decx}
For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
\end{lemma}

Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$, 
we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encodes $w$. Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, 
hence $\semof A$ is characterised by models of $\parikhof {A}$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof {A}$ does not constraint them), we may say that 
%\begin{lemma}\ref{lemma:decw}
%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\parikhfof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
%\end{lemma}
 $$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$$
where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}.

\paragraph{Synchronisation of PFA}
The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$, 
namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof {A}$ and $(I'\cup \pim')\in\parikhof {L(A')}$ such that 
$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.
